Plot previous findings

### 2024-07-13 code_data/previous_studies/PreviousFindings.Rmd
Updated via the Open Science Framework

```{r}
library(ggplot2)
library(tidyverse)
library(cowplot)
library(ggbreak)

# Van Dyke (2007) estimates from published paper:

## E1

### critical

@@

### spill-over

```{r}
## E1 spill-over

## not sig. Syn effect in E1 spill-over:
VD07E1spillSynmn <- (568+551)/2 - (571+566)/2
VD07E1spillSynSE <- 18 #highest SE in spill-over region, Table 3
VD07E1spillSynlower <- round(VD07E1spillSynmn - 2*VD07E1spillSynSE)
VD07E1spillSynupper <- round(VD07E1spillSynmn + 2*VD07E1spillSynSE)

@@

### Sentence-Final

```{r}
## E1 sentence-final

@@

## Experiment 2

### critical: SYN

```{r}
# Experiment 2 SYN in critical

## sig. Syn effect in E2 crit region FPRT:
VD07E2critSynFPRTmn <- (413+418)/2-(376+382)/2
VD07E2critSynFPRTtval <- sqrt(8.32)
VD07E2critSynFPRTSE <- VD07E2critSynFPRTmn/VD07E2critSynFPRTtval
VD07E2critSynFPRTlower <- round(VD07E2critSynFPRTmn - 2*VD07E2critSynFPRTSE)
VD07E2critSynFPRTupper <- round(VD07E2critSynFPRTmn + 2*VD07E2critSynFPRTSE)

@@

### critical: SEM

```{r}
# Experiment 2 Sem in critical

## non sig. Sem effect in E2 crit region FPRT:
VD07E2critSemFPRTmn <- (418+382)/2-(413+376)/2
VD07E2critSemFPRTtval <- sqrt(1.13)
VD07E2critSemFPRTSE <- VD07E2critSemFPRTmn/VD07E2critSemFPRTtval
VD07E2critSemFPRTlower <- round(VD07E2critSemFPRTmn - 2*VD07E2critSemFPRTSE)
VD07E2critSemFPRTupper <- round(VD07E2critSemFPRTmn + 2*VD07E2critSemFPRTSE)

@@

### critical: Int

```{r}
# Experiment 2 Int in critical

## non sig. Int effect in E2 crit region FPRT:
VD07E2critIntFPRTmn <- (418-413)-(382-376)
VD07E2critIntFPRTSE <- 21 #highest SE in critical region, Table 7
VD07E2critIntFPRTlower <- round(VD07E2critIntFPRTmn - 2*VD07E2critIntFPRTSE)
VD07E2critIntFPRTupper <- round(VD07E2critIntFPRTmn + 2*VD07E2critIntFPRTSE)

@@

### spill-over: SYN

```{r}
# Experiment 2 SYN in spill-over

## almost sig. Syn effect in E2 post-crit region FPRT (negative sign)
VD07E2postcritSynFPRTmn<-(325+296)/2-(320+364)/2
VD07E2postcritSynFPRTtval<-sqrt(6.58)
VD07E2postcritSynFPRTSE<-VD07E2postcritSynFPRTmn/VD07E2postcritSynFPRTtval
VD07E2postcritSynFPRTlower<-VD07E2postcritSynFPRTmn-2*VD07E2postcritSynFPRTSE
VD07E2postcritSynFPRTupper<-VD07E2postcritSynFPRTmn+2*VD07E2postcritSynFPRTSE

@@

### spill-over: Sem

```{r}
# Experiment 2 Sem in spill-over

## almost sig. Sem effect in E2 post-crit region FPRT (negative sign)
VD07E2postcritSemFPRTmn<- (296+364)/2-(325+320)/2
VD07E2postcritSemFPRTSE<- 21 #highest SE in spill-over region, Table 7
VD07E2postcritSemFPRTlower<-VD07E2postcritSemFPRTmn-2*VD07E2postcritSemFPRTSE
VD07E2postcritSemFPRTupper<-VD07E2postcritSemFPRTmn+2*VD07E2postcritSemFPRTSE

@@

### spill-over: Int

```{r}
# Experiment 2 Int in spill-over

## almost sig. Int effect in E2 post-crit region FPRT (negative sign)
VD07E2postcritIntFPRTmn<- (296-325)-(364-320)
VD07E2postcritIntFPRTtval<- sqrt(5.22)
VD07E2postcritIntFPRTSE<-VD07E2postcritIntFPRTmn/VD07E2postcritIntFPRTtval
VD07E2postcritIntFPRTlower<-VD07E2postcritIntFPRTmn-2*VD07E2postcritIntFPRTSE
VD07E2postcritIntFPRTupper<-VD07E2postcritIntFPRTmn+2*VD07E2postcritIntFPRTSE

@@

### Sentence-Final: SYN

```{r}
# Experiment 2 SYN in sentence-final region (Table 7)

## Syn effect in E2 sentence-final region FPRT 
VD07E2finalSynFPRTmn<-(259+271)/2-(286+274)/2
VD07E2finalSynFPRTSE<- 22 #highest SE in sentence-final region, Table 7
VD07E2finalSynFPRTlower<-VD07E2finalSynFPRTmn-2*VD07E2finalSynFPRTSE
VD07E2finalSynFPRTupper<-VD07E2finalSynFPRTmn+2*VD07E2finalSynFPRTSE

@@

### sentence-final: Sem

```{r}
# Experiment 2 Sem in sentence-final (Table 7)

## Sem effect in E2 sentence-final region FPRT
VD07E2finalSemFPRTmn<- (271+274)/2-(259+286)/2
VD07E2finalSemFPRTSE<- 22 #highest SE in sentence-final region, Table 7
VD07E2finalSemFPRTlower<-VD07E2finalSemFPRTmn-2*VD07E2finalSemFPRTSE
VD07E2finalSemFPRTupper<-VD07E2finalSemFPRTmn+2*VD07E2finalSemFPRTSE

@@

### sentence-final: Int

```{r}
# Experiment 2 Int in sentence-final (Table 7)

## Int effect in E2 sentence-final region FPRT
VD07E2finalIntFPRTmn<- (271-259)-(274-286)
VD07E2finalIntFPRTSE<- 22 #highest SE in sentence-final region, Table 7
VD07E2finalIntFPRTlower<-VD07E2finalIntFPRTmn-2*VD07E2finalIntFPRTSE
VD07E2finalIntFPRTupper<-VD07E2finalIntFPRTmn+2*VD07E2finalIntFPRTSE

@@

## Experiment 3  
### precrit: SYN

```{r}
# Experiment 3  SYN in pre-crit

## almost sig. Syn effect in E3 precrit region FPRT:
VD07E3precritSynFPRTmn <- (462+447)/2-(449+455)/2
VD07E3precritSynFPRTSE <- 18 #highest SE in pre-crit region, Table 16
VD07E3precritSynFPRTlower <- round(VD07E3precritSynFPRTmn-2*VD07E3precritSynFPRTSE)
VD07E3precritSynFPRTupper <- round(VD07E3precritSynFPRTmn+2*VD07E3precritSynFPRTSE)

@@

### precrit: SEM

```{r}
# Experiment 3  SEM in pre-crit

## almost sig. Sem effect in E3 precrit region FPRT:
VD07E3precritSemFPRTmn <- (455+447)/2-(449+462)/2
VD07E3precritSemFPRTSE <- 18 #highest SE in pre-crit region, Table 16
VD07E3precritSemFPRTlower <- round(VD07E3precritSemFPRTmn-2*VD07E3precritSemFPRTSE)
VD07E3precritSemFPRTupper <- round(VD07E3precritSemFPRTmn+2*VD07E3precritSemFPRTSE)

@@

### precrit: INT

```{r}
# Experiment 3  Int in pre-crit

## almost sig. Int effect in E3 precrit region FPRT:
VD07E3precritIntFPRTmn <- (447-462)-(455-449)
VD07E3precritIntFPRTSE <- 18 #highest SE in pre-crit region, Table 16
VD07E3precritIntFPRTlower <- round(VD07E3precritIntFPRTmn-2*VD07E3precritIntFPRTSE)
VD07E3precritIntFPRTupper <- round(VD07E3precritIntFPRTmn+2*VD07E3precritIntFPRTSE)

@@

## almost sig. Syn effect in E3 crit region TFT:
VD07E3critSynTFTmn <- (451+467)/2-(414+421)/2
VD07E3critSynTFTSE <- 38 #highest SE in crit region, Table 16
VD07E3critSynTFTlower <- round(VD07E3critSynTFTmn-2*VD07E3critSynTFTSE)
VD07E3critSynTFTupper <- round(VD07E3critSynTFTmn+2*VD07E3critSynTFTSE)

### crit: Sem 
```{r}
# Experiment 3  SEM in crit

## almost sig. Sem effect in E3 crit region FPRT:
VD07E3critSemFPRTmn <- (282+280)/2-(274+294)/2
VD07E3critSemFPRTSE <- 11 #highest SE in crit region, Table 16
VD07E3critSemFPRTlower <- round(VD07E3critSemFPRTmn-2*VD07E3critSemFPRTSE)
VD07E3critSemFPRTupper <- round(VD07E3critSemFPRTmn+2*VD07E3critSemFPRTSE)

@@

### crit: Int 
```{r}
# Experiment 3  Int in crit

## almost sig. Int effect in E3 crit region FPRT:
VD07E3critIntFPRTmn <- (280-294)-(282-274)
VD07E3critIntFPRTtval <- sqrt(3.34) # reported in paper as <3.35
VD07E3critIntFPRTSE <- VD07E3critIntFPRTmn/VD07E3critIntFPRTtval
VD07E3critIntFPRTlower <- round(VD07E3critIntFPRTmn-2*VD07E3critIntFPRTSE)
VD07E3critIntFPRTupper <- round(VD07E3critIntFPRTmn+2*VD07E3critIntFPRTSE)

@@

### spill-over: SYN

```{r}
# Experiment 3  SYN in postcrit

## almost sig. Syn effect in E3 postcrit region FPRT:
VD07E3postcritSynFPRTmn <- (424+442)/2-(437+448)/2
VD07E3postcritSynFPRTSE <- 24 #highest SE in spill-over region, Table 16
VD07E3postcritSynFPRTlower <- round(VD07E3postcritSynFPRTmn-2*VD07E3postcritSynFPRTSE)
VD07E3postcritSynFPRTupper <- round(VD07E3postcritSynFPRTmn+2*VD07E3postcritSynFPRTSE)

@@

## almost sig. Syn effect in E3 postcrit region TFT:
VD07E3postcritSynTFTmn <- (766+731)/2-(707+711)/2
VD07E3postcritSynTFTSE <- 59 #highest SE in spill-over region, Table 16
VD07E3postcritSynTFTlower <- round(VD07E3postcritSynTFTmn-2*VD07E3postcritSynTFTSE)
VD07E3postcritSynTFTupper <- round(VD07E3postcritSynTFTmn+2*VD07E3postcritSynTFTSE)

### spill-over: Sem 
```{r}
# Experiment 3  SEM in postcrit

## almost sig. Sem effect in E3 postcrit region FPRT:
VD07E3postcritSemFPRTmn <- (437+424)/2-(448+442)/2
VD07E3postcritSemFPRTSE <- 24 #highest SE in spill-over region, Table 16
VD07E3postcritSemFPRTlower <- round(VD07E3postcritSemFPRTmn-2*VD07E3postcritSemFPRTSE)
VD07E3postcritSemFPRTupper <- round(VD07E3postcritSemFPRTmn+2*VD07E3postcritSemFPRTSE)

@@

### spill-over: Int 
```{r}
# Experiment 3  Int in postcrit

## almost sig. Int effect in E3 postcrit region FPRT:
VD07E3postcritIntFPRTmn <- (424-442)-(437-448)
VD07E3postcritIntFPRTSE <-24 #highest SE in spill-over region, Table 16
VD07E3postcritIntFPRTlower <- round(VD07E3postcritIntFPRTmn-2*VD07E3postcritIntFPRTSE)
VD07E3postcritIntFPRTupper <- round(VD07E3postcritIntFPRTmn+2*VD07E3postcritIntFPRTSE)

@@

### sentence final: SYN

```{r}
# Experiment 3  SYN in sentence final region (Table 16 in VD07)

## almost sig. Syn effect in E3 final region FPRT:
VD07E3finalSynFPRTmn <- (463+483)/2-(480+464)/2
VD07E3finalSynFPRTtval <- sqrt(1.06) # reported in paper as below 1.07
VD07E3finalSynFPRTSE <- VD07E3finalSynFPRTmn/VD07E3finalSynFPRTtval
VD07E3finalSynFPRTlower <- round(VD07E3finalSynFPRTmn-2*VD07E3finalSynFPRTSE)
VD07E3finalSynFPRTupper <- round(VD07E3finalSynFPRTmn+2*VD07E3finalSynFPRTSE)

@@

## almost sig. Syn effect in E3 final region TFT:
VD07E3finalSynTFTmn <- (663+675)/2-(705+649)/2
VD07E3finalSynTFTtval <- sqrt(1.53) # reported in paper as below 1.54
VD07E3finalSynTFTSE <- VD07E3finalSynTFTmn/VD07E3finalSynTFTtval
VD07E3finalSynTFTlower <- round(VD07E3finalSynTFTmn-2*VD07E3finalSynTFTSE)
VD07E3finalSynTFTupper <- round(VD07E3finalSynTFTmn+2*VD07E3finalSynTFTSE)

@@

### Sentence-Final: Int 
```{r}
# Experiment 3  Int in final (Table 16 in VD07)

## Int effect in E3 final region FPRT:
VD07E3finalIntFPRTmn <- (463-483)-(480-464)
VD07E3finalIntFPRTtval <- sqrt(1.06) # reported in paper as below 1.07
VD07E3finalIntFPRTSE <- VD07E3finalIntFPRTmn/VD07E3finalIntFPRTtval
VD07E3finalIntFPRTlower <- round(VD07E3finalIntFPRTmn-2*VD07E3finalIntFPRTSE)
VD07E3finalIntFPRTupper <- round(VD07E3finalIntFPRTmn+2*VD07E3finalIntFPRTSE)

@@

VD07estimates$int_type <- factor(VD07estimates$int_type,levels=c("syntactic","semantic", "interaction"))

str(VD07estimates)
```

# Mertzen et al 2021:

```{r}
load("M21_byregionsummaries_de.rda")

M23.G <- d
M23.G$experiment <- "M23.G (N=121)"

@@

M23estimates <- M23estimates[,-4]
M23estimates <- M23estimates[,-5]
M23estimates <- M23estimates[,-6]

# Plot previous findings
```{r}
my_colors <- RColorBrewer::brewer.pal(11, "RdBu")

previous <- rbind(VD07estimates, M23estimates)
save(previous, file="VD07_M21_estimates.rda")

previous_crit.plot <- ggplot(subset(previous, previous$region%in%c("pre-critical","critical")),
                   aes(x=experiment, y=mean, ymin=lower, ymax=upper )) +
  geom_pointrange(aes(color=experiment, shape=measure), 
             size=0.5, position=position_dodge(0.9))+
  scale_shape_manual(values = c(18,16,17,15))+
  scale_color_manual(values = c(my_colors[3], my_colors[4],my_colors[5],my_colors[8],my_colors[9]))+
  geom_hline(yintercept=0, linetype="solid", alpha=.4)+
  ggh4x::facet_grid2(region ~ int_type, scales="free_y", independent = "y") +
  theme_bw(base_size = 10)+
  scale_x_discrete(breaks = NULL)+
  xlab("")+
  ylab("reading time difference (ms)")+
  #ggtitle("Previous findings")+
  guides(shape = guide_legend(order = 2),col = guide_legend(order = 1))

previous_crit.plot
ggsave("plots/previous_findings.jpg", width=6, height=5, dpi=600)
```

# Plot present and previous findings
```{r, eval=FALSE}
my_colors <- RColorBrewer::brewer.pal(11, "RdBu")

@@

# combine with previous estimates
estimates <- rbind(previous, SVestimates)
estimates$experiment <- factor(estimates$experiment, levels=c("VD07.E1 (N=35)", "VD07.E2 (N=36)", "VD07.E3 (N=40)", "M23.E (N=61)", "M23.G (N=121)", "present (N=774)"))

pp.plot <- ggplot(data=filter(estimates, region %in% c("pre-critical", "critical", "spill-over")),
                   aes(x=int_type, y=mean, ymin=lower, ymax=upper )) +
    geom_pointrange(aes(color=experiment, shape=measure), 
             size=0.8, position=position_dodge(1.45))+
  scale_shape_manual(values = c(18,16,17,15), breaks=c("SPR", "FPRT", "RPD", "TFT"),
                         labels=c("self-paced reading time", "first-pass reading time", "regression path duration", "total fixation time"))+
  scale_color_manual(values = c(my_colors[3], my_colors[4],my_colors[5],my_colors[8],my_colors[9], "black"))+
  geom_hline(yintercept=0, linetype="solid", alpha=.5)+
  facet_grid(region~int_type, scales="free", space="free") +
  theme_bw(base_size = 15)+
  scale_x_discrete(breaks = NULL)+
  theme(legend.position="right", legend.box="vertical", legend.direction="vertical")+
  xlab("")+
  ylab("reading time difference (ms)")+
  #ggtitle("Present and previous findings")+
  guides(shape = guide_legend(order = 2),col = guide_legend(order = 1))

RTs.plot <- pp.plot + coord_cartesian(ylim=c(-75, 150)) + ggtitle("Reading time differences") 
ggsave("plots/present_previous_findings.jpg", width=9, height=8, dpi=600)

pp2.plot <- ggplot(data=filter(estimates, region %in% c("pre-critical", "critical", "spill-over") & measure %in%c("SPR", "TFT")),
                   aes(x=int_type, y=mean, ymin=lower, ymax=upper )) +
    geom_pointrange(aes(color=experiment, shape=measure), 
             size=0.8, position=position_dodge(1.45))+
  scale_shape_manual(values = c(18,16,17,15), breaks=c("SPR", "FPRT", "RPD", "TFT"),
                         labels=c("self-paced reading time", "first-pass reading time", "regression path duration", "total fixation time"))+
  scale_color_manual(values = c(my_colors[3], my_colors[4],my_colors[5],my_colors[8],my_colors[9], "black"))+
  geom_hline(yintercept=0, linetype="solid", alpha=.5)+
  facet_grid(region~int_type, scales="free", space="free") +
  theme_bw(base_size = 15)+
  scale_x_discrete(breaks = NULL)+
  theme(legend.position="right", legend.box="vertical", legend.direction="vertical")+
  xlab("")+
  ylab("reading time difference (ms)")+
  #ggtitle("Present and previous findings")+
  guides(shape = guide_legend(order = 2),col = guide_legend(order = 1))

pp2.plot + coord_cartesian(ylim=c(-50, 100))  
ggsave("plots/present_previous_findings_SPR_TFT.jpg", width=9, height=8, dpi=600)

>>>>

```{r}
library(ggplot2)
library(tidyverse)
library(cowplot)
```

# Van Dyke (2007) estimates from published paper:
## E1 
### critical

@@

### spill-over
```{r}
## E1 spill-over
## not sig. Syn effect in E1 spill-over:
VD07E1spillSynmn <- (568+551)/2 - (571+566)/2
VD07E1spillSynSE <- 18 #highest SE in spill-over region, Table 3
VD07E1spillSynlower <- round(VD07E1spillSynmn - 2*VD07E1spillSynSE)
VD07E1spillSynupper <- round(VD07E1spillSynmn + 2*VD07E1spillSynSE)

@@

### Sentence-Final
```{r}
## E1 sentence-final

@@

## Experiment 2
### critical: SYN 
```{r}
# Experiment 2 SYN in critical
## sig. Syn effect in E2 crit region FPRT:
VD07E2critSynFPRTmn <- (413+418)/2-(376+382)/2
VD07E2critSynFPRTtval <- sqrt(8.32)
VD07E2critSynFPRTSE <- VD07E2critSynFPRTmn/VD07E2critSynFPRTtval
VD07E2critSynFPRTlower <- round(VD07E2critSynFPRTmn - 2*VD07E2critSynFPRTSE)
VD07E2critSynFPRTupper <- round(VD07E2critSynFPRTmn + 2*VD07E2critSynFPRTSE)

@@

### critical: SEM
```{r}
# Experiment 2 Sem in critical
## non sig. Sem effect in E2 crit region FPRT:
VD07E2critSemFPRTmn <- (418+382)/2-(413+376)/2
VD07E2critSemFPRTtval <- sqrt(1.13)
VD07E2critSemFPRTSE <- VD07E2critSemFPRTmn/VD07E2critSemFPRTtval
VD07E2critSemFPRTlower <- round(VD07E2critSemFPRTmn - 2*VD07E2critSemFPRTSE)
VD07E2critSemFPRTupper <- round(VD07E2critSemFPRTmn + 2*VD07E2critSemFPRTSE)

@@

### critical: Int
```{r}
# Experiment 2 Int in critical
## non sig. Int effect in E2 crit region FPRT:
VD07E2critIntFPRTmn <- (418-413)-(382-376)
VD07E2critIntFPRTSE <- 21 #highest SE in critical region, Table 7
VD07E2critIntFPRTlower <- round(VD07E2critIntFPRTmn - 2*VD07E2critIntFPRTSE)
VD07E2critIntFPRTupper <- round(VD07E2critIntFPRTmn + 2*VD07E2critIntFPRTSE)

@@

### spill-over: SYN 
```{r}
# Experiment 2 SYN in spill-over
## almost sig. Syn effect in E2 post-crit region FPRT (negative sign)
VD07E2postcritSynFPRTmn<-(325+296)/2-(320+364)/2
VD07E2postcritSynFPRTtval<-sqrt(6.58)
VD07E2postcritSynFPRTSE<-VD07E2postcritSynFPRTmn/VD07E2postcritSynFPRTtval
VD07E2postcritSynFPRTlower<-VD07E2postcritSynFPRTmn-2*VD07E2postcritSynFPRTSE
VD07E2postcritSynFPRTupper<-VD07E2postcritSynFPRTmn+2*VD07E2postcritSynFPRTSE

@@

### spill-over: Sem 
```{r}
# Experiment 2 Sem in spill-over
## almost sig. Sem effect in E2 post-crit region FPRT (negative sign)
VD07E2postcritSemFPRTmn<- (296+364)/2-(325+320)/2
VD07E2postcritSemFPRTSE<- 21 #highest SE in spill-over region, Table 7
VD07E2postcritSemFPRTlower<-VD07E2postcritSemFPRTmn-2*VD07E2postcritSemFPRTSE
VD07E2postcritSemFPRTupper<-VD07E2postcritSemFPRTmn+2*VD07E2postcritSemFPRTSE

@@

### spill-over: Int 
```{r}
# Experiment 2 Int in spill-over
## almost sig. Int effect in E2 post-crit region FPRT (negative sign)
VD07E2postcritIntFPRTmn<- (296-325)-(364-320)
VD07E2postcritIntFPRTtval<- sqrt(5.22)
VD07E2postcritIntFPRTSE<-VD07E2postcritIntFPRTmn/VD07E2postcritIntFPRTtval
VD07E2postcritIntFPRTlower<-VD07E2postcritIntFPRTmn-2*VD07E2postcritIntFPRTSE
VD07E2postcritIntFPRTupper<-VD07E2postcritIntFPRTmn+2*VD07E2postcritIntFPRTSE

@@

### Sentence-Final: SYN 
```{r}
# Experiment 2 SYN in sentence-final region (Table 7)
## Syn effect in E2 sentence-final region FPRT 
VD07E2finalSynFPRTmn<-(259+271)/2-(286+274)/2
VD07E2finalSynFPRTSE<- 22 #highest SE in sentence-final region, Table 7
VD07E2finalSynFPRTlower<-VD07E2finalSynFPRTmn-2*VD07E2finalSynFPRTSE
VD07E2finalSynFPRTupper<-VD07E2finalSynFPRTmn+2*VD07E2finalSynFPRTSE

@@

### sentence-final: Sem 
```{r}
# Experiment 2 Sem in sentence-final (Table 7)
## Sem effect in E2 sentence-final region FPRT
VD07E2finalSemFPRTmn<- (271+274)/2-(259+286)/2
VD07E2finalSemFPRTSE<- 22 #highest SE in sentence-final region, Table 7
VD07E2finalSemFPRTlower<-VD07E2finalSemFPRTmn-2*VD07E2finalSemFPRTSE
VD07E2finalSemFPRTupper<-VD07E2finalSemFPRTmn+2*VD07E2finalSemFPRTSE

@@

### sentence-final: Int 
```{r}
# Experiment 2 Int in sentence-final (Table 7)
## Int effect in E2 sentence-final region FPRT
VD07E2finalIntFPRTmn<- (271-259)-(274-286)
VD07E2finalIntFPRTSE<- 22 #highest SE in sentence-final region, Table 7
VD07E2finalIntFPRTlower<-VD07E2finalIntFPRTmn-2*VD07E2finalIntFPRTSE
VD07E2finalIntFPRTupper<-VD07E2finalIntFPRTmn+2*VD07E2finalIntFPRTSE

@@

## Experiment 3  
### precrit: SYN
```{r}
# Experiment 3  SYN in pre-crit
## almost sig. Syn effect in E3 precrit region FPRT:
VD07E3precritSynFPRTmn <- (462+447)/2-(449+455)/2
VD07E3precritSynFPRTSE <- 18 #highest SE in pre-crit region, Table 16
VD07E3precritSynFPRTlower <- round(VD07E3precritSynFPRTmn-2*VD07E3precritSynFPRTSE)
VD07E3precritSynFPRTupper <- round(VD07E3precritSynFPRTmn+2*VD07E3precritSynFPRTSE)

@@

### precrit: SEM
```{r}
# Experiment 3  SEM in pre-crit
## almost sig. Sem effect in E3 precrit region FPRT:
VD07E3precritSemFPRTmn <- (455+447)/2-(449+462)/2
VD07E3precritSemFPRTSE <- 18 #highest SE in pre-crit region, Table 16
VD07E3precritSemFPRTlower <- round(VD07E3precritSemFPRTmn-2*VD07E3precritSemFPRTSE)
VD07E3precritSemFPRTupper <- round(VD07E3precritSemFPRTmn+2*VD07E3precritSemFPRTSE)

@@

### precrit: INT
```{r}
# Experiment 3  Int in pre-crit
## almost sig. Int effect in E3 precrit region FPRT:
VD07E3precritIntFPRTmn <- (447-462)-(455-449)
VD07E3precritIntFPRTSE <- 18 #highest SE in pre-crit region, Table 16
VD07E3precritIntFPRTlower <- round(VD07E3precritIntFPRTmn-2*VD07E3precritIntFPRTSE)
VD07E3precritIntFPRTupper <- round(VD07E3precritIntFPRTmn+2*VD07E3precritIntFPRTSE)

@@

## almost sig. Syn effect in E3 crit region TFT:
VD07E3critSynTFTmn <- (451+467)/2-(414+421)/2
VD07E3critSynTFTSE <- 38 #highest SE in crit region, Table 16
VD07E3critSynTFTlower <- round(VD07E3critSynTFTmn-2*VD07E3critSynTFTSE)
VD07E3critSynTFTupper <- round(VD07E3critSynTFTmn+2*VD07E3critSynTFTSE)
```

### crit: Sem 
```{r}
# Experiment 3  SEM in crit
## almost sig. Sem effect in E3 crit region FPRT:
VD07E3critSemFPRTmn <- (282+280)/2-(274+294)/2
VD07E3critSemFPRTSE <- 11 #highest SE in crit region, Table 16
VD07E3critSemFPRTlower <- round(VD07E3critSemFPRTmn-2*VD07E3critSemFPRTSE)
VD07E3critSemFPRTupper <- round(VD07E3critSemFPRTmn+2*VD07E3critSemFPRTSE)

@@

### crit: Int 
```{r}
# Experiment 3  Int in crit
## almost sig. Int effect in E3 crit region FPRT:
VD07E3critIntFPRTmn <- (280-294)-(282-274)
VD07E3critIntFPRTtval <- sqrt(3.34) # reported in paper as <3.35
VD07E3critIntFPRTSE <- VD07E3critIntFPRTmn/VD07E3critIntFPRTtval
VD07E3critIntFPRTlower <- round(VD07E3critIntFPRTmn-2*VD07E3critIntFPRTSE)
VD07E3critIntFPRTupper <- round(VD07E3critIntFPRTmn+2*VD07E3critIntFPRTSE)

@@

### spill-over: SYN
```{r}
# Experiment 3  SYN in postcrit
## almost sig. Syn effect in E3 postcrit region FPRT:
VD07E3postcritSynFPRTmn <- (424+442)/2-(437+448)/2
VD07E3postcritSynFPRTSE <- 24 #highest SE in spill-over region, Table 16
VD07E3postcritSynFPRTlower <- round(VD07E3postcritSynFPRTmn-2*VD07E3postcritSynFPRTSE)
VD07E3postcritSynFPRTupper <- round(VD07E3postcritSynFPRTmn+2*VD07E3postcritSynFPRTSE)

@@

## almost sig. Syn effect in E3 postcrit region TFT:
VD07E3postcritSynTFTmn <- (766+731)/2-(707+711)/2
VD07E3postcritSynTFTSE <- 59 #highest SE in spill-over region, Table 16
VD07E3postcritSynTFTlower <- round(VD07E3postcritSynTFTmn-2*VD07E3postcritSynTFTSE)
VD07E3postcritSynTFTupper <- round(VD07E3postcritSynTFTmn+2*VD07E3postcritSynTFTSE)
```

### spill-over: Sem 
```{r}
# Experiment 3  SEM in postcrit
## almost sig. Sem effect in E3 postcrit region FPRT:
VD07E3postcritSemFPRTmn <- (437+424)/2-(448+442)/2
VD07E3postcritSemFPRTSE <- 24 #highest SE in spill-over region, Table 16
VD07E3postcritSemFPRTlower <- round(VD07E3postcritSemFPRTmn-2*VD07E3postcritSemFPRTSE)
VD07E3postcritSemFPRTupper <- round(VD07E3postcritSemFPRTmn+2*VD07E3postcritSemFPRTSE)

@@

### spill-over: Int 
```{r}
# Experiment 3  Int in postcrit
## almost sig. Int effect in E3 postcrit region FPRT:
VD07E3postcritIntFPRTmn <- (424-442)-(437-448)
VD07E3postcritIntFPRTSE <-24 #highest SE in spill-over region, Table 16
VD07E3postcritIntFPRTlower <- round(VD07E3postcritIntFPRTmn-2*VD07E3postcritIntFPRTSE)
VD07E3postcritIntFPRTupper <- round(VD07E3postcritIntFPRTmn+2*VD07E3postcritIntFPRTSE)

@@

### sentence final: SYN
```{r}
# Experiment 3  SYN in sentence final region (Table 16 in VD07)
## almost sig. Syn effect in E3 final region FPRT:
VD07E3finalSynFPRTmn <- (463+483)/2-(480+464)/2
VD07E3finalSynFPRTtval <- sqrt(1.06) # reported in paper as below 1.07
VD07E3finalSynFPRTSE <- VD07E3finalSynFPRTmn/VD07E3finalSynFPRTtval
VD07E3finalSynFPRTlower <- round(VD07E3finalSynFPRTmn-2*VD07E3finalSynFPRTSE)
VD07E3finalSynFPRTupper <- round(VD07E3finalSynFPRTmn+2*VD07E3finalSynFPRTSE)

@@

## almost sig. Syn effect in E3 final region TFT:
VD07E3finalSynTFTmn <- (663+675)/2-(705+649)/2
VD07E3finalSynTFTtval <- sqrt(1.53) # reported in paper as below 1.54
VD07E3finalSynTFTSE <- VD07E3finalSynTFTmn/VD07E3finalSynTFTtval
VD07E3finalSynTFTlower <- round(VD07E3finalSynTFTmn-2*VD07E3finalSynTFTSE)
VD07E3finalSynTFTupper <- round(VD07E3finalSynTFTmn+2*VD07E3finalSynTFTSE)
```

@@

### Sentence-Final: Int 
```{r}
# Experiment 3  Int in final (Table 16 in VD07)
## Int effect in E3 final region FPRT:
VD07E3finalIntFPRTmn <- (463-483)-(480-464)
VD07E3finalIntFPRTtval <- sqrt(1.06) # reported in paper as below 1.07
VD07E3finalIntFPRTSE <- VD07E3finalIntFPRTmn/VD07E3finalIntFPRTtval
VD07E3finalIntFPRTlower <- round(VD07E3finalIntFPRTmn-2*VD07E3finalIntFPRTSE)
VD07E3finalIntFPRTupper <- round(VD07E3finalIntFPRTmn+2*VD07E3finalIntFPRTSE)

@@

VD07estimates$int_type <- factor(VD07estimates$int_type,levels=c("syntactic","semantic", "interaction"))
```

# Mertzen et al 2023: 
```{r}
load("M21_byregionsummaries_de.rda")
M23.G <- d
M23.G$experiment <- "M23.G (N=121)"

@@

M23estimates <- M23estimates %>% select(-lang, -region.label, -effect)
```

# Plot present and previous findings
```{r}
my_colors <- RColorBrewer::brewer.pal(11, "RdBu")

@@

# combine with previous estimates
estimates <- rbind(VD07estimates, M23estimates, SVestimates)
estimates$experiment <- factor(estimates$experiment, levels=c("VD07.E1 (N=35)", "VD07.E2 (N=36)", "VD07.E3 (N=40)", "M23.E (N=61)", "M23.G (N=121)", "present (N=774)"))

RT_plot <- ggplot(data=filter(estimates, region %in% c("pre-critical", "critical", "spill-over")),
                       aes(x=int_type, y=mean, ymin=lower, ymax=upper )) +
                  geom_pointrange(aes(color=experiment, shape=measure), 
                       size=0.8, position=position_dodge(1.45))+
                  scale_shape_manual(values = c(18,16,17,15), breaks=c("SPR", "FPRT", "RPD", "TFT"),
                                     labels=c("self-paced reading time", "first-pass reading time", "regression path duration", "total fixation time"))+
                  scale_color_manual(values = c(my_colors[3], my_colors[4],my_colors[5],my_colors[8],my_colors[9], "black"))+
                  geom_hline(yintercept=0, linetype="solid", alpha=.5)+
                  facet_grid(region~int_type, scales="free", space="free") +
                  theme_bw(base_size = 15)+
                  scale_x_discrete(breaks = NULL)+
                  theme(legend.position="right", legend.box="vertical", legend.direction="vertical")+
                  xlab("")+
                  ylab("reading time difference (ms)")+
                  #ggtitle("Present and previous findings")+
                  guides(shape = guide_legend(order = 2),col = guide_legend(order = 1))+
                  coord_cartesian(ylim=c(-75, 150)) +
                  ggtitle("Reading time differences") 
ggsave("plots/present_previous_findings.jpg", width=9, height=8, dpi=600)

TFT_plot <- ggplot(data=filter(estimates, region %in% c("pre-critical", "critical", "spill-over") & measure %in%c("SPR", "TFT")), aes(x=int_type, y=mean, ymin=lower, ymax=upper )) +
                  geom_pointrange(aes(color=experiment, shape=measure), 
                           size=0.8, position=position_dodge(1.45))+
                scale_shape_manual(values = c(18,16,17,15), breaks=c("SPR", "FPRT", "RPD", "TFT"),
                                       labels=c("self-paced reading time", "first-pass reading time", "regression path duration", "total fixation time"))+
                scale_color_manual(values = c(my_colors[3], my_colors[4],my_colors[5],my_colors[8],my_colors[9], "black"))+
                geom_hline(yintercept=0, linetype="solid", alpha=.5)+
                facet_grid(region~int_type, scales="free", space="free") +
                theme_bw(base_size = 15)+
                scale_x_discrete(breaks = NULL)+
                theme(legend.position="right", legend.box="vertical", legend.direction="vertical")+
                xlab("")+
                ylab("reading time difference (ms)")+
                #ggtitle("Present and previous findings")+
                guides(shape = guide_legend(order = 2),col = guide_legend(order = 1))+
                coord_cartesian(ylim=c(-50, 100))  
ggsave("plots/present_previous_findings_SPR_TFT.jpg", width=9, height=8, dpi=600)
